---
title: 'Worksheet #5'
author: "Quennie Tabladillo"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

1.The table shows the enrollment of BS in Computer Science,SY 2010-2011.

a. Plot the data using a bar graph. Write the codes and copy the result.
```{r Course, echo=TRUE}
one <- c("1st", "2nd","3rd","4th")
two <- c(80,75,70,60)
barplot((two), 
  ylab = "2019-2020",
  xlab = "Course Year",
  names.arg = c("1st", "2nd","3rd","4th"))
```

b. Using the same table, label the barchart with
Title = ” Enrollment of BS Computer Science
horizontal axis = “Curriculum Year” and
vertical axis = “number of students”
```{r enrollment, echo = TRUE}
one <- c("1st", "2nd","3rd","4th")
two <- c(80,75,70,60)
barplot((two), 
        main = "Enrollment of BS Computer Science",
        ylab = "number of students",
        xlab = "Curriculum Year",
        names.arg = c("1st", "2nd","3rd","4th"))
```

2. The monthly income of De Jesus family was spent on the following:
  60% on Food, 10% on electricity, 5% for savings, and
25% for other miscellaneous expenses.

a. Create a table for the above scenario.
```{r table, echo = FALSE}
#Write the codes and its result.
de <- c("60%","10%","5%","25%")
jesus <- c("Food", "electricity", "savings","miscellaneous expenses")
k <- table((de), 
           names.arg = c("Food", "electricity", "savings","miscellaneous expenses"))
k
```

b. Plot the data using a pie chart. Add labels, colors and legend.
```{r Pie, echo = FALSE}
#Write the codes and its result.
de <- c(60,10,5,25)
de 
pie(de)

jesus <- c("Food", "electricity", "savings","miscellaneous expenses")
k <- table((de), 
           names.arg = c("Food", "electricity", "savings","miscellaneous expenses"))

de_jesus <- round(de/sum(de) * 100, 1)
de_jesus <- paste(de_jesus, "%", sep = "")
pie(de, main = "Expenses", col = rainbow(length(de)), labels = de_jesus, cex = 0.5)

legend(1.0,0.5, c("Food", "electricity", "savings","miscellaneous expenses"),
       cex = 0.5, fill = rainbow((length(de_jesus))))
```

3.Open mtcars dataset.
```{r 3}
data(mtcars)
```

a.Create a simple histogram specifically for mpg (miles per gallon) variable.

Use $ to select the mpg only. Write the codes and its result.
```{r 3a}
hist(mtcars$mpg)
```

b.Colored histogram with different number of bins.
hist(mtcars$mpg, breaks=12, col="red")
Note: breaks= controls the number of bins
```{r 3b}
mtcarsDF <- c(mtcars$mpg)
hist(mtcars$mpg, breaks=12, col="red")
```

c.Add a Normal Curve
Copy the result
```{r 3c}
x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
        main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)
```

4. Open the iris dataset. Create a subset for each species.

a. Write the codes and its result
```{r 4a}
data("iris")
iris
seto <- subset(iris, Species == "setosa")
seto
versi <- subset(iris, Species == "versicolor")
versi
virgi <- subset(iris, Species == "virginica")
virgi
```

b. Get the mean for every characteristics of each species using colMeans().
Write the codes and its result.
Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])
```{r 4b}
setosa <- colMeans(seto[sapply(iris,is.numeric)])
setosa
virginica <- colMeans(versi[sapply(iris,is.numeric)])
virginica
versicolor <- colMeans(virgi[sapply(iris,is.numeric)])
versicolor
```

c. Combine all species by using rbind()
```{r 4c}
table <- rbind(setosa,versicolor,virginica)
table
```

d. From the data in 4-c: Create the barplot().
```{r 4d}
#Write the codes and its result
table <- rbind(setosa,versicolor,virginica)
table
barplot(table, beside = TRUE,
                main = "Iris Mean",
                xlab = "Characteristics",
                ylab = "Mean Scores",
                col = c("red","green","blue"))
```