---
title: "Worksheet 4"
author: "Quennie Tabladillo"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

>1. The table shows the data about shoe size and height.Create a data frame.
```{r 1}
Customers <- data.frame(
  Shoesize = c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,
              7.5,10.5,8.5,12.0,10.5,
              13.0,11.5,8.5,5.0,10.0,
             6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0),
  Height = c(66.0,68.0,64.5,65.0,70.0,
            64.0,70.0,71.0,72.0,64.0,
            74.5,67.0,71.0,71.0,77.0,72.0,
            59.0,62.0,72.0,66.0,64.0,67.0,73.0,
            69.0,72.0,70.0,69.0,70),
  Gender = c("F","F","F","F","M","F","M","F","M",
            "M","M","F","M","M","M","M","F","F",
            "M","F","M","M","M","F","M","M","M","M")
)
Customers
```
a.Describe the data.
```{r 1a}
#The data is about the customers shoe size, height and gender.
```

b.Find the mean of shoe size and height of the respondents.
```{r 1b}
#Copy the codes and results
summary(Customers)
#Shoesize:    Mean   : 9.411
#Height:      Mean   :68.57
```

c. Is there a relationship between shoe size and height? Why?
```{r 1c}
#Yes,because taller women tend to have larger feet since they need a larger
#base for balance while shorter women tend to have smaller feet since 
#they require a smaller base.
```

2.Construct character vector months to a factor with factor() and assign
the result to factor_months_vector. Print out factor_months_vector and 
assert that R prints out the factor levels below the actual values.
```{r 2}
Months <- c("March","April","January","November","January",
            "September","October","September","November","August",
            "January","November","November","February","May","August",
            "July","December","August","August","September","November","February","April")
factor_Months <- factor(Months)
factor_Months
```

3.Then check the summary() of the months_vector and factor_months_vector.
Interpret the results of both vectors. Are they both equally
useful in this case?
```{r 3}
summary(Months)
summary(factor_Months)
```

4.Create a vector and factor for the table below.
```{r 4}
factor_data <- c(1,4,3)
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```

5. Enter the data below in Excel with file name = import_march.csv

a.Import the excel file into the environment pane using read.table() function
```{r 5a}
getwd()
readdata <- read.table("import_march.csv", header = TRUE, sep = ",")
readdata
```
b. View thee data set.Write the code and its result.
```{r b}
read.csv("import_march.csv")
```


















