---
title: "Worksheet _Tabladillo#6"
author: "Quennie Tabladillo"
date: "2022-11-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r mpg, include = TRUE}
library(ggplot2)
library(dplyr)
data(mpg)
mpg
```

>1. How many columns are in mpg dataset? How about the number of rows? Show the
codes and its result.

```{r 1, include = TRUE}
#Number of column in mpg dataset
ncol(mpg)
#Number of rows in mpg dataset
nrow(mpg)
```

>2.Which manufacturer has the most models in this data set? Which model has the
most variations?

```{r 2, include = TRUE}
#Manufacturer with the most models
data1 <- mpg %>% group_by(manufacturer) %>% count() 
data1
#Model with the most variations
data2 <- mpg %>% group_by(model) %>% count()
data2
#Ans: The manufacturer with the most models is "dodge" and the model with the most
#variations is the "caravan 2wd"
```

>a.Group the manufacturers and find the unique models. Copy the codes and result.

```{R 2a, include = TRUE}
unique1 <- mpg %>% group_by(manufacturer, model) %>% distinct %>% count()
colnames(unique1) <- c("Manufacturer","Model","Counts")
unique1
```

>b.Graph the result by using plot() and ggplot(). Write the codes and its result

```{r 2b, echo = TRUE}
plot(unique1)
ggplot(unique1, aes(Model, Manufacturer)) + geom_point()
```

>3. Same dataset will be used. You are going to show the relationship of the 
model and the manufacturer

>a.What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?

```{r 3a, echo = TRUE}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

>b.For you, is it useful? If not, how could you modify the data to make it more
informative?

```{r 3b}
#Ans: The plot is not useful for a number of reasons
#Each dot represents a different manufacturer-model combination that we observe in the data.
#Some of the data is hidden as some manufacturer-model combinations appear
#more than once in the data (e.g. `audi a4 quattro`)
```

>4.Using the pipe (%>%), group the model and get the number of cars per model.
Show codes and its result

```{r 4, echo = FALSE}
model <- mpg %>% group_by(model) %>% count()
model

colnames(model) <- c("Model","Counts")
model
```

>a.Plot using the geom_bar() + coord_flip() just like what is shown below. Show
codes and its result

```{r 4a, echo = TRUE}
qplot(model,data = mpg,main = "Number of Cars
per Model", xlab = "Model",ylab = "Number
of Cars", geom = "bar", fill = manufacturer) +
  coord_flip()
```

>b.Use only the top 20 observations. Show code and results

```{r 4b, echo = TRUE}
topObserve <- mpg %>% group_by(model) %>% tally(sort = TRUE)
topObserve
ggplot(topObserve, aes(x = model, y = n, fill = "gray")) + 
  geom_bar(stat = "identity") + coord_flip()
```

>5. Plot the relationship between cyl - number of cylinders and displ - engine 
displacement using geom_point with aesthetic colour = engine displacement. 
Title should be “Relationship between No. of Cylinders and Engine Displacement”.

>a. Show the codes and its result.

```{r 5a, echo = TRUE}
ggplot(mpg, aes(x = displ, y = cyl)) + geom_point(aes(colour =
"engine displacement")) +
labs(title = "Relationship between No of Cylinders and Engine Displacement") + 
geom_jitter()
```

>b. How would you describe its relationship?

```{r 5b, include = TRUE}
#As the number of  cylinder increases, the engine displacement also increases.
```

>6.Get the total number of observations for drv - type of drive train 
(f = front-wheel drive,r = rear wheel drive, 4 = 4wd) and class - type of class 
(Example: suv, 2seater, etc.).
Plot using the geom_tile() where the number of observations for class be used as a
fill for aesthetics.

>a. Show the codes and its result for the narrative in #6.

```{r 6a, echo = TRUE}
ggplot(mpg, aes(x = drv, y = class)) + geom_tile(aes(fill = class))
```

>b.Interpret the result.

```{r 6b, include = TRUE}
#Ans: The suv are both under the 4 wheel drive and the rear wheel drive, while
#the subcompact,pick up, midsize and the compact fall under the 4 wheel drive only.
#The minivan fall under the front wheel drive and the 2seater fall under the rear wheel drive.
```

>7.  Discuss the difference between these codes. Its outputs for each are shown below.

```{r 7, echo = TRUE}
#Code 1
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
#Code 2
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")

#Ans: The difference between the two codes are the color of the dots in the
#plot although, based on the two codes the color that was declared was blue.
```

>8. Try to run the command ?mpg. What is the result of this command?
?mpg

```{r 8, include = TRUE}
#Ans: The result was the R documentation of a dataset about the fuel economy 
#data from 1999 to 2008 for 38 popular models of car
```

>a.Which variables from mpg dataset are categorical?

```{r 8a, include =TRUE}
#Ans: Categorical variables in mpg include: manufacturer, model, trans (type of transmission), drv (front-wheel drive, rear-wheel, 4wd), fl (fuel type), and class (type of car).
```

>b. Which are continuous variables?

```{r 8b, include = TRUE}
#Ans: cty , city highway miles per gallon
```

>c. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped
it with a continuous variable you have identified in #5-b. What is its result? Why it produced such
output?

```{r 8c, echo = TRUE}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()

#Ans: The plot shows a negative relationship between engine size (displ) and 
#fuel efficiency (hwy). In other words, cars with big engines use more fuel.
```

>9. Plot the relationship between displ(engine displacement) and hwy(highway miles per gallon) using
geom_point(). Add a trend line over the existing plot using geom_smooth() with se = FALSE. Default
method is “loess”.

```{r 9, echo = TRUE}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color=class)) +
  geom_smooth()
```

>10. Using the relationship of displ and hwy, add a trend line over existing plot. Set these = FALSE to
remove the confidence interval and method = lm to check for linear modeling

```{r 10, echo = TRUE} 
ggplot(mpg, aes(x = displ, y = hwy, color = class)) + 
  geom_point(aes(color=class)) + 
  geom_smooth(se = FALSE)
```
