---
title: 'Worksheet #7a'
author: "Quennie Tabladillo"
date: "2022-12-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##R Markdown


>1. Create a data frame for the table below.

```{r 1}
Student_Scores <- data.frame(
  Student = c(1:10),
  Pre_test = c(55,54,47,57,51,61,57,54,63,58),
  Post_test = c(61,60,56,63,56,63,59,56,62,61)
)
Student_Scores
```

>a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.

```{r 1a}
library(Hmisc)
library(pastecs)
```

```{r 1descstat}
describe(Student_Scores)
stat.desc(Student_Scores)
```

>2.The Department of Agriculture was studying the effects of several levels of a
fertilizer on the growth of a plant. For some analyses, it might be useful to convert
the fertilizer levels to an ordered factor.

>a. the data were 10,10,10, 20,20,50,10,20,10,50,20,50,20,10.

```{r 2a}
fertilizer <- c(10,10,10,20,20,50,10,
                20,10,50,20,50,20,10)

fertilizer_factor <- factor(fertilizer, ordered = TRUE)
fertilizer_factor
```

>3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study
the exercise levels undertaken by 10 num3 were “l”, “n”, “n”, “i”, “l” ,
“l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense

>a. What is the best way to represent this in R?

```{r 3a}
exercise_levels <- c("l","n","n","i","l","l","n","n","i","l")

data.frame(exercise_levels)
```

>4.Sample of 30 tax accountants from all the states and territories of Australia and
their individual state of origin is specified by a character vector of state mnemonics
as:

```{r 4} 
 state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
             "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
             "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
             "vic", "vic", "act")
```
>a. Apply the factor function and factor level. Describe the results.

```{r 4a}
australia <- factor(state)
australia
```

 >5.From #4 - continuation:
 Suppose we have the incomes of the same tax accountants in another vector (in
suitably large units of money)

```{r 5}
 incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
```

>a.Calculate the sample mean income for each state we can now use the special 
function tapply():

```{r 5a} 
sample_5 <- tapply(incomes, state, mean)
sample_5 
```

>b.Copy the results and interpret

```{r 5b}
#results
#act       nsw       nt      qld       sa      tas      vic       wa 
#44.50000  57.33333 55.50000 53.60000 55.00000 60.50000 56.00000 52.25000 
#the results shows the mean of every level of income for each state.
```

>6. Calculate the standard errors of the state income means (refer again to number 3)

>a. What is the standard error? Write the codes.

```{r 6a}
standard_err.n <- length(sample_5)
standard_err.sd <- sd(sample_5)
standard_err.se <- standard_err.sd/sqrt(standard_err.n)
standard_err.se
```

>b. Interpret the result

```{r 6b}
#This is how I get the state income means by dividing the sd() to sqrt() or length() 
#and that is how I get the standard errors of the state income means and this was 
#the result.
```

>7. Use the titanic dataset

>a.Subset the titanic dataset of those who survived and not survived. Show the
codes and its result.

```{r 7 a}
data("Titanic")
Titanic <- data.frame(Titanic)

survived <- subset(Titanic, Survived == "Yes")
survived

not_survived <- subset(Titanic, Survived == "No")
not_survived
```

>8.The data sets are about the breast cancer Wisconsin. The samples arrive
periodically as Dr. Wolberg reports his clinical cases. The database therefore
reflects this chronological grouping of the data.
You can create this dataset in Microsoft Excel.

>a.describe what is the dataset all about.

```{r 8a}
#Answer: The dataset is all about the breast cancer Wisconsin.
```

>b.Import the data from MS Excel.Copy the codes.

```{r 8b}
library("readxl")

Breast_cancer <- read_excel("E:/CS 101/Worksheet 7a/Breast_Cancer.xlsx")
```

>c. Compute the descriptive statistics using different packages. Find the values of:

>c.1 Standard error of the mean for clump thickness.

```{r 8c1}
Breast_cancerc1.n <- length(Breast_cancer$'CL. thickness')
Breast_cancerc1.sd <- sd(Breast_cancer$'CL. thickness')
Breast_cancerc1.se <- Breast_cancerc1.sd/sqrt(Breast_cancer$'CL. thickness')
Breast_cancerc1.se
```

>c.2 Coefficient of variability for Marginal Adhesion.

```{r 8c2}
sd(Breast_cancer$`Marg. Adhesion`) / mean(Breast_cancer$`Marg. Adhesion`) * 100
```

>c.3 Number of null values of Bare Nuclei

```{r 8c3}
Breast_cancerc3 <- subset(Breast_cancer,`Bare. Nuclei` == "NA")
Breast_cancerc3
```

>c.4 Mean and standard deviation for Bland Chromatin

```{r 8c4}
mean(Breast_cancer$'Bl. Cromatin')
sd(Breast_cancer$'Bl. Cromatin')
```

>c.5 Confidence interval of the mean for Uniformity of Cell Shape
Calculate the mean

```{r 8c5}
breast_cancerc5 <- mean(Breast_cancer$`Cell Shape`)
breast_cancerc5

#Calculate the standard error of the mean
numA <- length(Breast_cancer$`Cell Shape`)
numB <- sd(Breast_cancer$`Cell Shape`)
numC <- numB/sqrt(numA)
numC

#Find the t-score that corresponds to the confidence level
numD = 0.05
numE = numA - 1
numF = qt(p=numD/2, df=numE,lower.tail=F)
numF

#Constructing the confidence interval
numG <- numF * numC
numG
#Lower
numH <- breast_cancerc5 - numG
numH
#Upper
numI <- breast_cancerc5 + numG
numI

c(numH,numI)
```

>d. How many attributes?

```{r 8d}
attributes(Breast_cancer)
```

>e. Find the percentage of respondents who are malignant. Interpret the results.

```{r 8e}
cancer <- subset(Breast_cancer, Class == "malignant")
cancer

17 / 49 * 100

#There are 34.69388 or 35% of respondents who are malignant.
```

>9.Export the data abalone to the Microsoft excel file. Copy the codes

```{r 9}
library("AppliedPredictiveModeling")
data(abalone)
head(abalone)
summary(abalone)

#exporting the data abalone

library(xlsx)

write.xlsx("abalone","C:\\Users\\Quennie\\Documents\\abalone.xlsx")
```










































































































































































































































































